\documentclass[a4paper, 14pt]{article}

\usepackage{soul}
\usepackage{titlesec}
\usepackage{setspace}

% package for lists
\usepackage{enumitem}
% reduce space before list
\setlist{nolistsep}

% lists geometry
\let\olditemize\itemize
\renewcommand{\itemize}{
  \olditemize
  \setlength{\itemsep}{-8pt}
  \setlength{\parskip}{-8pt}
  \setlength{\parsep}{-8pt}
}

% line spacing
\onehalfspacing

% margins
\usepackage[total={5in, 8.7in}]{geometry}

% this is a global declaration that changes the appearance of the section command
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}

\begin{document}

\begin{center}
	\textsc{\Huge{\so{Ivan Sergienko}}}
\end{center}

\section{Brief Summary}
	Php/Js homegrown developer with experience of making websites with basic functionality. \\
	I like coding in Vim; writing clean, easy to read/understand code; top-down design; solving interesting problems.
\section{Experiences}
	2012-2014:\\
	Developing simple websites by myself, for tiny companies. \\
	I wrote around 8 websites from scratch, mostly using CodeIgniter php framework. \\
	Problems I worked on: \\
	\vspace{-1.5em}
	\begin{itemize}
		\item interface for customer to edit website content.\\
		\item e-shop cart for making online orders.\\
		\item simple databases for products / website content. \\
		\item js, css animation; js/php form validation; ajax.
	\end{itemize}
\section{Skills}
	Php\&mysql, javascript (+jquery, +angular) - upper beginner :) \\
	Git, linux, vim - beginner \\
	MVC pattern \\
  CodeIgniter php framework \\
  Symfony, Doctrine - a little bit \\
\section{Projects \& Code Examples}
	Check out my CodeIgniter based tiny eShop at \\
    https://bitbucket.org/DarthVanger/spyoptics.kiev.ua/src
	% (my PHP can be found in src/application/models/ ) \\
	% (my JS can be found in src/assets/js/ )
\section{Education}
	3 years in Kiev Polytechnic Institute, Applied physics. \\
	Stanford programming methodology course (15 hours of lectures on youtube). \\
	Epam Java web development course (100 hours in classroom). \\
	w3schools.com, php.net, stackoverflow :)
\section{Languages}
	English - Upper Intermediate (around 7/10, both spoken and written).
\section{Contact}
	tel. 093 078 01 38 \\
	email: ivan.sergiienko@gmail.com \\
	website: vanger.kiev.ua
\section{Personal Info}
	Age: 23 years \\
	Residence: Kiev
\end{document}
